---
title: "Bayesian Network"
output: html_document
---

###### Bayesian Network model

####Load relevant packages

```{r}
install.packages("bnlearn")
install.packages("Rgraphviz")
install.packages("bnviewer")
```

```{r}
library("bnlearn")
library("Rgraphviz")
library("bnviewer")
```

###Bayesian Network Model
# Version `Knowledge' 
```{r}
######Bayesian Model Part
#Model 1: Knowledge about each other


###Graph Structure

dag = model2network("[NormalityA][NormalityB][AexpectsB|NormalityB][BexpectsA|NormalityA][MentalStateA][MentalStateB][ActionA|NormalityA:AexpectsB:MentalStateA][ActionB|NormalityB:BexpectsA:MentalStateB][Outcome|ActionA:ActionB]")

###Variables

NormalityA.lv = c("F", "T")
NormalityB.lv = c("F", "T")
AexpectsB.lv = c("F", "T")
BexpectsA.lv = c("F", "T")
MentalStateA.lv = c("F", "T")
MentalStateB.lv = c("F", "T")
ActionA.lv = c("F", "T")
ActionB.lv = c("F", "T")
Outcome.lv = c("F", "T")

###Conditional Probablities

NormalityA.prob = array(c(0.2, 0.8), dim = 2, dimnames = list(NormalityA = NormalityA.lv))
NormalityB.prob = array(c(0.2, 0.8), dim = 2, dimnames = list(NormalityB = NormalityB.lv))
AexpectsB.prob = array(c(0.9, 0.1, 0.1, 0.9), dim = c(2,2), dimnames = list(AexpectsB = AexpectsB.lv, NormalityB= NormalityB.lv))
BexpectsA.prob = array(c(0.9, 0.1, 0.1, 0.9), dim = c(2,2), dimnames = list(BexpectsA = BexpectsA.lv, NormalityA= NormalityA.lv))
MentalStateA.prob = array(c(0.9, 0.1), dim = 2, dimnames = list(MentalStateA = MentalStateA.lv))
MentalStateB.prob = array(c(0.9, 0.1), dim = 2, dimnames = list(MentalStateB = MentalStateB.lv))
ActionA.prob = array(c(0.8, 0.2, 0.9,0.1, 0.8, 0.2,0.1,0.9,0.2,0.8,0.9,0.1, 0.2, 0.8, 0.1,0.9), dim = c(2, 2, 2, 2), dimnames = list(ActionA=ActionA.lv, AexpectsB = AexpectsB.lv, MentalStateA = MentalStateA.lv, NormalityA = NormalityA.lv))
ActionB.prob = array(c(0.8, 0.2, 0.9,0.1, 0.8, 0.2,0.1,0.9,0.2,0.8,0.9,0.1, 0.2, 0.8, 0.1,0.9), dim = c(2, 2, 2, 2), dimnames = list(ActionB=ActionB.lv, BexpectsA = BexpectsA.lv, MentalStateB = MentalStateB.lv, NormalityB = NormalityB.lv))
Outcome.prob = array(c(1, 0, 1, 0, 1, 0, 0, 1), dim = c(2,2, 2), dimnames = list(Outcome = Outcome.lv, ActionA=ActionA.lv, ActionB=ActionB.lv))

cpt = list(NormalityA = NormalityA.prob, 
             NormalityB = NormalityB.prob,
             AexpectsB = AexpectsB.prob,
             BexpectsA = BexpectsA.prob,
             MentalStateA=MentalStateA.prob,
             MentalStateB=MentalStateB.prob,
             ActionA=ActionA.prob,
             ActionB=ActionB.prob,
             Outcome=Outcome.prob)
      
###set up model        
survey = custom.fit(dag, cpt)

### plot model
graphviz.plot(dag,shape = "ellipse")

```

#Estimation of Conditional Probablity for mental state
```{r}
#############Mental State

##### Mental State for Abnormal Agent
## mental state true
M_Abnormal<-cpquery(survey, event = (MentalStateB == "T"), evidence = (NormalityA == "T") & 
          (NormalityB == "F") & (ActionA == "T") &(ActionB == "T") &(Outcome == "T"), n=10000000 )


#### Mental State for Normal Agent
## mental state true
M_Normal<-cpquery(survey, event = (MentalStateA == "T"), evidence = (NormalityA == "T") & 
          (NormalityB == "F") & (ActionA == "T") & (ActionB == "T") , n=10000000 )

```

#Estimation of Conditional Probablity for epistemic state
```{r}
#############Epistemic State

##### Epistemic State for Abnormal Agent
## epistemic  state true
E_Abnormal<-cpquery(survey, event = (BexpectsA == "T"), evidence = (NormalityA == "T") & 
          (NormalityB == "F") & (ActionA == "T") & (ActionB == "T") &(Outcome == "T"), n=10000000 )

#### Epistemic State for Normal Agent
## epistemic  state true
E_Normal<-cpquery(survey, event = (AexpectsB == "T"), evidence = (NormalityA == "T") & 
          (NormalityB == "F") & (ActionA == "T") & (ActionB == "T") , n=10000000 )
```

#create dataframe with cpqs
```{r}

df.Knowledge<-data.frame(Prediction=c(M_Abnormal, M_Normal, E_Abnormal, E_Normal), Condition=c("Agent 2: abnormal", "Agent 1: normal", "Agent 2: abnormal", "Agent 1: normal"), InferenceType=c("Mental State", "Mental State", "Expectation about other agent", "Expectation about other agent")) %>% 
  mutate(Prediction = round(Prediction, digits=2)) %>% 
  mutate(Knowledge = "Knowledge")

```

#Plots for model predictions `Knowledge'

```{r}
####Graph Predictions:

#set theme
myTheme <-   theme(plot.title=element_text(size=18, 
                                    face="bold", 
                                    hjust=0.5,
                                    lineheight=1.2),
                   axis.title.x  = element_blank(), 
                   axis.title.y = element_text(color="black", size = 18, vjust=.9), 
                   axis.text.x = element_text(color="black", size = 14),
                   axis.text.y = element_text(color="black", size = 18), 
                   strip.text.x = element_text(color="black", size = 16),
                   legend.text = element_text(color="black", size = 18),
                   legend.title = element_text(color="black", size = 18),
                   legend.position = "top",
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))

#set colour palette 
ecPalette<-c("gray13", "khaki4")

#create plot
FigXa <-df.Knowledge %>% 
  mutate(Condition =factor(Condition,levels=c("Agent 1: normal", "Agent 2: abnormal"))) %>% 
  ggplot(aes(x=factor(Condition), Prediction, fill=Condition)) +
  geom_bar(stat="identity", position = "dodge", colour = "black", alpha=0.6)+
  coord_cartesian(ylim = c(0,1.1)) +
  geom_text(aes(label=scales::percent(Prediction, accuracy = 1)),  vjust=-0.6, color="black", size=6)+
  labs( y="Probablity")+
  scale_y_continuous(labels =scales::percent_format(accuracy = 1), breaks = seq(0, 1, by=0.25))+
  scale_fill_manual(values = ePalette)+
  facet_grid(~InferenceType)+
  theme_bw()+
  myTheme+
  theme(legend.position= "none")+
  labs(title="Knowledge")

###show plot
plot(FigXa)
```

###Bayesian Network Model
# Version `No Knowledge' 
```{r}
# Version `No Knowledge' 

#Graph Structure
 dag2 = model2network("[NormalityA][NormalityB][AexpectsB][BexpectsA][MentalStateA][MentalStateB][ActionA|NormalityA:AexpectsB:MentalStateA][ActionB|NormalityB:BexpectsA:MentalStateB][Outcome|ActionA:ActionB]")

#Variables

NormalityA.lv = c("F", "T")
NormalityB.lv = c("F", "T")
AexpectsB.lv = c("F", "T")
BexpectsA.lv = c("F", "T")
MentalStateA.lv = c("F", "T")
MentalStateB.lv = c("F", "T")
ActionA.lv = c("F", "T")
ActionB.lv = c("F", "T")
Outcome.lv = c("F", "T")

#Conditional  probabilities

NormalityA.prob = array(c(0.2, 0.8), dim = 2, dimnames = list(NormalityA = NormalityA.lv))
NormalityB.prob = array(c(0.2, 0.8), dim = 2, dimnames = list(NormalityB = NormalityB.lv))
AexpectsB.prob = array(c(0.9, 0.1), dim = 2, dimnames = list(AexpectsB = AexpectsB.lv)) #### independent node
BexpectsA.prob = array(c(0.9, 0.1), dim = 2, dimnames = list(BexpectsA = BexpectsA.lv)) #### independent node
MentalStateA.prob = array(c(0.9, 0.1), dim = 2, dimnames = list(MentalStateA = MentalStateA.lv))
MentalStateB.prob = array(c(0.9, 0.1), dim = 2, dimnames = list(MentalStateB = MentalStateB.lv))
ActionA.prob = array(c(0.8, 0.2, 0.9,0.1, 0.8, 0.2,0.1,0.9,0.2,0.8,0.9,0.1, 0.2, 0.8, 0.1,0.9), dim = c(2, 2, 2, 2), dimnames = list(ActionA=ActionA.lv, AexpectsB = AexpectsB.lv, MentalStateA = MentalStateA.lv, NormalityA = NormalityA.lv))
ActionB.prob = array(c(0.8, 0.2, 0.9,0.1, 0.8, 0.2,0.1,0.9,0.2,0.8,0.9,0.1, 0.2, 0.8, 0.1,0.9), dim = c(2, 2, 2, 2), dimnames = list(ActionB=ActionB.lv, BexpectsA = BexpectsA.lv, MentalStateB = MentalStateB.lv, NormalityB = NormalityB.lv))
Outcome.prob = array(c(1, 0, 1, 0, 1, 0, 0, 1), dim = c(2,2, 2), dimnames = list(Outcome = Outcome.lv, ActionA=ActionA.lv, ActionB=ActionB.lv))

cpt2 = list(NormalityA = NormalityA.prob, 
             NormalityB = NormalityB.prob,
             AexpectsB = AexpectsB.prob,
             BexpectsA = BexpectsA.prob,
             MentalStateA=MentalStateA.prob,
             MentalStateB=MentalStateB.prob,
             ActionA=ActionA.prob,
             ActionB=ActionB.prob,
             Outcome=Outcome.prob)

#Set up model
survey2 = custom.fit(dag2, cpt2)

# plot model
graphviz.plot(dag2,shape = "ellipse")

```

#Estimation of Conditional Probablity for mental state

```{r}
#############Mental State
##### Mental State for Abnormal Agent
## mental state true
M_Abnormal2<-cpquery(survey2, event = (MentalStateB == "T"), evidence = (NormalityA == "T") & 
          (NormalityB == "F") & (ActionA == "T") &(ActionB == "T") &(Outcome == "T"), n=10000000 )


#### Mental State for Normal Agent
## mental state true
M_Normal2<-cpquery(survey2, event = (MentalStateA == "T"), evidence = (NormalityA == "T") & 
          (NormalityB == "F") & (ActionA == "T") & (ActionB == "T") , n=10000000 )
```

#Estimation of Conditional Probablity for epistemic state

```{r}
##### Epistemic State for Abnormal Agent
## epistemic  state true
E_Abnormal2<-cpquery(survey2, event = (BexpectsA == "T"), evidence = (NormalityA == "T") & 
          (NormalityB == "F") & (ActionA == "T") & (ActionB == "T") &(Outcome == "T"), n=10000000 )

#### Epistemic State for Normal Agent
## epistemic  state true
E_Normal2<-cpquery(survey2, event = (AexpectsB == "T"), evidence = (NormalityA == "T") & 
          (NormalityB == "F") & (ActionA == "T") & (ActionB == "T") , n=10000000 )
```

#create dataframe with cpqs

```{r}

df.NoKnowledge<-data.frame(Prediction=c(M_Abnormal2, M_Normal2, E_Abnormal2, E_Normal2), Condition=c("Agent 2: abnormal", "Agent 1: normal", "Agent 2: abnormal", "Agent 1: normal"), InferenceType=c("Mental State", "Mental State", "Expectation about other agent", "Expectation about other agent")) %>% 
  mutate(Prediction = round(Prediction, digits=2)) %>% 
  mutate(Knowledge="No Knowledge")

```

#Plot model predictions `No Knowledge'
```{r}

####Set theme
myTheme <-   theme(plot.title=element_text(size=18, 
                                    face="bold", 
                                    hjust=0.5,
                                    lineheight=1.2),
                   axis.title.x  = element_blank(), 
                   axis.title.y = element_text(color="black", size = 18, vjust=.9), 
                   axis.text.x = element_text(color="black", size = 14),
                   axis.text.y = element_text(color="black", size = 18), 
                   strip.text.x = element_text(color="black", size = 16),
                   legend.text = element_text(color="black", size = 18),
                   legend.title = element_text(color="black", size = 18),
                   legend.position = "top",
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))
 
#set colour palette   
ePalette<- c("#969696", "#f7f7f7")

#create plot
FigXb <- df.NoKnowledge %>% 
  mutate(Condition =factor(Condition,levels=c("Agent 1: normal", "Agent 2: abnormal"))) %>% 
  ggplot(aes(x=factor(Condition), Prediction, fill=Condition)) +
  geom_bar(stat="identity", position = "dodge", colour = "black", alpha=0.6)+
  coord_cartesian(ylim = c(0,1.1)) +
  geom_text(aes(label=scales::percent(Prediction, accuracy = 1)), size=6, vjust=-0.6, color="black")+
  labs( y="Probablity")+
  scale_y_continuous(labels =scales::percent_format(accuracy = 1), breaks = seq(0, 1, by=0.25))+
  scale_fill_manual(values = ePalette)+
  facet_grid(~InferenceType)+
  theme_bw()+
  myTheme+
  theme(legend.position= "none")+
    labs(title="No Knowledge")


###show plot
plot(FigXb)
```

##create one plot wit predictions from 
#`Knowledge' and `No Knowledge' version
```{r}
#create plot
FigX <- ggarrange(FigXa, FigXb,
                    ncol = 1, 
                    nrow = 2)
#show plot
plot(FigX)

#save plot
ggsave(FigX, file="FigX.pdf", dpi=400, height = 8, width = 8)
ggsave(FigX, file="FigX.jpeg", dpi=400, height = 8, width = 8)

```